Musical Genres as Fuzzy Categories

### 2025-05-06 Old/analysis-proj.qmd
do it

```{r import data and select genre stereotype variables}
   #importing data
   dat <- read_dta("C:/Users/Omar Lizardo/Google Drive/MISC DATA SOURCES/SSI-2012/SSI2012.dta")
   #replacing ids with character names
   dat <- bind_cols(tibble(id_char = paste("id", sapply(dat[, 1], as.character), sep = "_")), dat) %>% 
   select(id_char, classicalfemale:hvymtluc, -ends_with("none")) %>%  #selecting relevant columns
   na.omit() #removing missing values
   head(dat)
```

>>>>

```{r import data and select genre stereotype variables}
   #importing data
   dat <- read_dta("C:/Users/Omar Lizardo/Google Drive/MISC DATA SOURCES/SSI-2012/SSI2012.dta")
   #replacing ids with character names
   dat <- bind_cols(tibble(id_char = paste("id", sapply(dat[, 1], as.character), sep = "_")), dat) %>% 
   select(id_char, classicalfemale:hvymtluc, -ends_with("none")) %>%  #selecting relevant columns
   na.omit() #removing missing values
```

### 2025-05-06 heidelberg-slides.qmd
do it

## Individual Matrix Examples (Two Mode)
:::: {.columns}
::: {.column width="50%"}
![id_65](Plots/data-ex1.png)
:::
::: {.column width="50%"}
![id_236](Plots/data-ex2.png)
:::
::::

## Individual Matrix Examples (Two Mode)
:::: {.columns}
::: {.column width="50%"}
![id_1114](Plots/data-ex3.png)
:::
::: {.column width="50%"}
![id_2002](Plots/data-ex4.png)
:::
::::

## Example Row Projection
:::: {.columns}
::: {.column width="50%"}
![id_65](Plots/data-ex1.png)
:::
::: {.column width="50%"}
![id_65](Plots/data-ex1-rp.png)
:::
::::

##  Example Column Projection
:::: {.columns}
::: {.column width="50%"}
![id_65](Plots/data-ex1.png)
:::
::: {.column width="50%"}
![id_65](Plots/data-ex1-cp.png)
:::
::::

##  Example Row Projection
:::: {.columns}
::: {.column width="50%"}
![id_236](Plots/data-ex2.png)
:::
::: {.column width="50%"}
![id_236](Plots/data-ex2-rp.png)
:::
::::

##  Example Column Projection
:::: {.columns}
::: {.column width="50%"}
![id_65](Plots/data-ex2.png)
:::
::: {.column width="50%"}
![id_65](Plots/data-ex2-cp.png)
:::
::::

@@

@@

@@

>>>>

## Individual Matrix Examples 
:::: {.columns}
::: {.column width="50%"}
![id_65 Affiliation Matrix](Plots/data-ex-af1.png)
:::
::: {.column width="50%"}
![id_236 Affiliation Matrix](Plots/data-ex-af2.png)
:::
::::

## Individual Matrix Examples 
:::: {.columns}
::: {.column width="50%"}
![id_1114 Affiliation Matrix](Plots/data-ex-af3.png)
:::
::: {.column width="50%"}
![id_2002 Affiliation Matrix](Plots/data-ex-af4.png)
:::
::::

## Example Row Projection
:::: {.columns}
::: {.column width="50%"}
![id_65 Affiliation Matrix](Plots/data-ex-af1.png)
:::
::: {.column width="50%"}
![id_65 Row Projection](Plots/data-ex-rp1.png)
:::
::::

##  Example Column Projection
:::: {.columns}
::: {.column width="50%"}
![id_65 Affiliation Matrix](Plots/data-ex-af1.png)
:::
::: {.column width="50%"}
![id_65 Column Projection](Plots/data-ex-cp1.png)
:::
::::

##  Example Row Projection
:::: {.columns}
::: {.column width="50%"}
![id_236 Affiliation Matrix](Plots/data-ex-af2.png)
:::
::: {.column width="50%"}
![id_236 Row Projection](Plots/data-ex-rp2.png)
:::
::::

##  Example Column Projection
:::: {.columns}
::: {.column width="50%"}
![id_236 Affiliation Matrix](Plots/data-ex-af2.png)
:::
::: {.column width="50%"}
![id_236 Column Projection](Plots/data-ex-cp2.png)
:::
::::

##  Example Row Backbone
:::: {.columns}
::: {.column width="50%"}
![id_65 Row Projection](Plots/data-ex-rp1.png)
:::
::: {.column width="50%"}
![id_65 Row Backbone](Plots/data-ex-rbb1.png)
:::
::::

##  Example Row Backbone
:::: {.columns}
::: {.column width="50%"}
![id_236 Row Projection](Plots/data-ex-rp2.png)
:::
::: {.column width="50%"}
![id_236 Row Backbone](Plots/data-ex-rbb2.png)
:::
::::

##  Example Column Backbone
:::: {.columns}
::: {.column width="50%"}
![id_65 Column Projection](Plots/data-ex-cp1.png)
:::
::: {.column width="50%"}
![id_65 Column Backbone](Plots/data-ex-cbb1.png)
:::
::::

##  Example Column Backbone
:::: {.columns}
::: {.column width="50%"}
![id_236 Column Projection](Plots/data-ex-cp2.png)
:::
::: {.column width="50%"}
![id_236 Column Backbone](Plots/data-ex-cbb2.png)
:::
::::

@@

## CA Eigenvalue Scree Plot
:::: {.columns}
::: {.column width="50%"}
![Stacked Genres](Plots/scree-genres.png)
:::
::: {.column width="50%"}
![Stacked Labels](Plots/scree-labels.png)
:::
::::

@@

## Correspondence Plot of Genre Clouds
![First and Second Dimensions](Plots/genre-proto-ex4.png)

## Correspondence Plot of Genre Clouds
![First and Second Dimensions](Plots/genre-proto-ex5.png)

## Correspondence Plot of Genre Clouds
![First and Second Dimensions](Plots/genre-proto-ex6.png)

## Correspondence Plot of Genre Clouds
![First and Second Dimensions](Plots/genre-proto-ex7.png)

@@

## Correspondence Plot of Label Clouds
![First and Second Dimensions](Plots/label-proto-ex5.png)

## Ridge Plot of Genre Clouds
![First Dimension](Plots/genre-ridge-dim1.png)

## Ridge Plot of Genre Clouds
![Second Dimension](Plots/genre-ridge-dim2.png)

## Ridge Plot of Genre Clouds
![Third Dimension](Plots/genre-ridge-dim3.png)

## Ridge Plot of Label Clouds
![First Dimension](Plots/label-ridge-dim1.png)

## Ridge Plot of Label Clouds
![Second Dimension](Plots/label-ridge-dim2.png)

## Ridge Plot of Label Clouds
![Third Dimension](Plots/label-ridge-dim3.png)

## Cloud Variance
:::: {.columns}
::: {.column width="47%"}
![Genres](Plots/genre-var.png)
:::
::: {.column width="47%"}
![Labels](Plots/label-var.png)
:::
::::

## Cloud Skewness
:::: {.columns}
::: {.column width="47%"}
![Skewness of Genres (Dim 1)](Plots/genre-skew1.png)
:::
::: {.column width="47%"}
![Skewness of Genres (Dim 2)](Plots/genre-skew2.png)
:::
::::

## Cloud Kurtosis
:::: {.columns}
::: {.column width="47%"}
![Kurtosis of Genres (Dim 1)](Plots/genre-kurt1.png)
:::
::: {.column width="47%"}
![Kurtosis of Genres (Dim 2)](Plots/genre-kurt2.png)
:::
::::
::::

## Cloud Skewness
:::: {.columns}
::: {.column width="47%"}
![Skewness of Labels (Dim 1)](Plots/label-skew1.png)
:::
::: {.column width="47%"}
![Skewness of Labels (Dim 2)](Plots/label-skew2.png)
:::
::::

## Cloud Kurtosis
:::: {.columns}
::: {.column width="47%"}
![Kurtosis of Labels (Dim 1)](Plots/label-kurt1.png)
:::
::: {.column width="47%"}
![Kurtosis of Labels (Dim 2)](Plots/label-kurt2.png)
:::
::::
::::
